### 2014-01-15 src/paper.Rnw
update

Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion. He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)

@@

$ \mu_\{M_{all} | M_{sdl}\} = 0 + \Sexpr{sdl.est} \times M_{sdl} \text{ with } R^2 = \Sexpr{sdl.r} $

@@

$ \mu_\{M_{all} | M_{rnd}\} = 0 + \Sexpr{rnd.est} \times M_{rnd}  \text{ with } R^2 = \Sexpr{rnd.r} $

@@

TODO: We should check if the distribution significantly different too.
TODO: Use sampling
TODO: Check on randoop samples too
TODO: Implement bomb (athrow) and see its mutation score, and see how close it comes.

>>>>

Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion. He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)
This was carried forward by Deng et al\cite{deng2013empirical}, (according to whom, random sampling was weak when it was made low enough for appreciable mutant savings). They realize a mean mutation score of 92\% for adequate test suites with SDL alone, and generating a saving of 81\% in the number of mutants, and 41\% fewer equivalent mutants.

Zhang et al.\cite{zhang2010operator}, compares operator based mutant selection to random mutant selection. They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin et al. against random mutant selection, with equal mutant probability, and equal mutagen probaiblity. They find that none of these selection techniques are superior to random selection, with same number of mutants. They also find that equal mutation sampling is more effective for larger subjects compared to equal mutagen sampling and the reverse is true for smaller subjects.
A second paper by Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator based mutant selection. They find that sampling strategies based on programming elements (method based) performed best.
% Baseline : x\% from selected set
% MOP : x\% from each mutagen
% for these, it is sampled from operator based selected set.
% PLEm : x\% from inside the same program element.
% PLE + MOP: sample x\% from same mutagen from same element.

@@

<<>>=
c <- cor(subset(m, select=c(mut.avg.sdl, mut.avg)) , method="kendall", use="pairwise")['mut.avg.sdl', 'mut.avg']
d <- cor(subset(m, select=c(mut.avg.rnd, mut.avg)) , method="kendall", use="pairwise")['mut.avg.rnd', 'mut.avg']
@

$ \mu_\{M_{all} | M_{sdl}\} = \Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = \Sexpr{sdl.r} \text{,} \tau_{\beta} = \Sexpr{c}$

@@

$ \mu_\{M_{all} | M_{rnd}\} = \Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = \Sexpr{rnd.r} \text{,} \tau_{\beta} = \Sexpr{d}$

@@

\begin{enumerate}
\item [TODO] We should check if the distribution significantly different too.
\item [TODO] Use sampling
\item [TODO] Check on randoop samples too
\item [TODO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [TODO] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODO] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}
